Busch, Khakhalin. Intrinsic temporal tuning

### 2019-06-06 reviews and responses.md

> Page 5, line 45/46: “As one possible explanation, auditory and mechanosensory inputs may have
different cellular or subcellular 46 targets in the tectum (Bollmann and Engert, 2009).”
This Bollmann and Engert reference does not address mechanosensory and auditory inputs. This paper
shows that the RGC inputs form a topographic map along the proximal-distal axis of individual tectal
neuron dendrites. This reference should be replaced with an appropriate reference.

> Also, how can having different subcellular targets could explain the results? This concept needs to be
clarified – an example would be helpful.

We replaced this sentence with the following one: "This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum (Pratt and Aizenman, 2009; Felch et al., 2016; Truszkowski et al., 2017), potentially leading to different recruitment of tectal excitatory and inhibitory circuits. Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree (Hiramoto and Cline, 2009; Deeg et al., 2009), which may shape their influence on neuronal plasticity (Richards and Lillicrap, 2019)."

Here, the actual rationale for the second explanation (a difference in subcellular targets) is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity, and neuronal tuning, respectively. Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, and the impact of inputs to the apical dendrites of pyramidal cells in the cortex. We feel, however, that this topic is very complex, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition into it by a short sentence and a good, recent reference.

SILAS-SAYS: For the climbing fiber to purkinje cell example, it may be worth noting that the climbing fiber makes hundreds of synapses along pretty much all of the primary dendritic arbor of the purkinje cell. So It doesn't really represent a spatially specific input to the dendritic arbor, except that there aren't really as many CF inputs to the distal most dendrites, so it is slightly proximal leaning. Also, I'm reading a paper now by Davie, Clark, and Hausser 2008 where they use DC to show that CF mediated dendritic spikes don't actually influence the axosomatic generated complex spike. Instead the huge Ca influx from CF input mediates LTD at Parallel fiber-purkinje cell synapses, so it is absolutely a great example to show the importance of calcium dynamics mediated by dendritic input on plasticity.

@@

> Page 13 line 46: The authors use the term “distributed sensory network” . Is a “distributed” network a
special type of sensory network?

Technically, even two neurons form a network (and a true mathematician would probably argue that even one neuron forms a network!), yet the tectal network is a relatively large one, with broad recurrent excitation, and in which different parts of the sensory input are processed in parallel. To subtly remind the reader about that, we used a word "distributed", as in "distributed computations", as opposed to more local and covergent networks, such as, for example, the Mauthner cell network in the hindbrain. This word is often used in writing (a Google Scholar search for `"distributed network" brain` returns 27000 hits), but admittedly it is not a precisely defined term, but rather a useful qualifier. If you think that this word is not appropriate here, please let us know, and we will remove it.

> Page 3, line 26,27,28: “In the tadpole tectum, looming stimuli are known to elicit stronger responses
compared to instantaneous inversions, yet the suppression yielded by looming stimuli was weaker”.
The logic of this sentence is not clear. Why exactly would the authors not expect that the looming
stimuli that is known to elicit stronger (synaptic?) responses would also cause less suppression (of action
potentials?) than does flashes?

This was unexpected as intrinsic plasticity is often described as a homeostatic mechanism. Thus a stronger stimulus could, in principle, cause stronger suppression of spiking. To make this point more clear, we now changed this sentence:

### 2019-06-06 reviews and responses.md

Here we are not implying that our conditional stimuli altered the pattern of synaptic inputs; rather, we refer to the fact that _during_ the stimulation, shorter stimuli (such as instantaneous flashes, which technically makes them the shortest stimuli possible) would cause faster visual inputs to the tectum, compared to longer, continuous transitions (second-long looms). Within this study, we did not measure actual synaptic responses in the tectum during conditioning, but from previous studies, we know that responses to flashes are indeed much shorter than responses to looming stimuli (Khakhalin 2014, Khakhalin 2019). We refer to these studies in the beginning of the "Results" section, and then again in the "Methods".

For page 5, we now changed the wording, to make this logic clearer.

"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al. 2014) would selectively suppress spiking in response to faster synaptic inputs."

SILAS-SAYS: While I think you answered the question, I don't think R2 will like the change. I think they want us to write in the text something like this: "As previous studies show that synaptic responses to flashes are much shorter than responses to looming stimuli in the tectum (Khakhalin 2014, Khakhalin 2019), and changes in intrinsic properties seemed homeostatic (ie increased activation led to reduced spiking), one could expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs." This uses your response to the reviewer to write what may be a clearer version of that particular sentence. When I get to the manuscript I will make a note about this comment at that place.

@@

Our measurements of spiking output relied on dynamic clamp experiments, in which we used simulated synaptic inputs, and not real synaptic stimulation. It means that any changes in spiking output we report in this paper are necessarily coming from the change in intrinsic properties. While a change in the strength of synaptic inputs  in response to sensory stimulation is possible, and indeed was observed and investigated in later sections of this paper, it would not have affected the number of spikes we reported in figures 1 and 2, as they were recorded in dynamic clamp experiments.

With the new wording of this sentence, we tried to make this point more clear:

"As changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to shorter sensory stimuli (instantaneous flashes; Khakhalin et al. 2014) would selectively suppress spiking in response to faster synaptic inputs."

SILAS-SAYS: My suggestion for this sentence, in the comment above, does not help to elaborate this point that R2 brings up, but I'm also not sure if your rewrite is resolving the confusion of R2. Maybe we just need an additional sentence before the problem sentence saying something along these lines: "One could expect that, if activity can induce a homeostatic suppression of excitability, then a specific profile of activity, such as a short duration, may cause a calibrated homeostatic suppression of a cell's excitability to that specific input profile."

@@

> Page 5 line 15: Does the word “preferred” (in quotes) mean that the cells fired more action potentials?
Maybe refrain from personification.

We hope that the word "prefer" is intuitive, and it has a benefit of being way shorter than "responded with more spikes", or "produced more action potentials", which hopefully makes reading easier. Realistically, we hope that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are intentionally a bit more relaxed when writing about cells, channels, receptors etc. Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use. Overall, we use the word "prefer" 6 times in the paper, always in the same way: when comparing spiking responses to different stimuli, to describe the stimulus that produced sronger outputs in a given set of neurons.

SILAS-SAYS: I'm kinda with the reviewer on this one. I agree that it's nice to use a potentially more intuitive word that shortens things, but at the very least I think we should explicitely state that prefered here means spiked more ("While control neurons produced increasing spikes in response to increasing input durations, exhibiting a preference for long synaptic inputs, neurons exposed to flashes..." ). Another issue R2 may be feeling but not saying explicitely is that in saying prefered, we seem to be suggesting a specific hypothesis about the goal of intrinsic plasticity of intrinsic excitability (ie retuning contributes something specific to the intake and export of information in a tectal neuron). Of course, we think that it is very important, but we don't have follow up experiments displaying what specific affects tectal retuning could have on sensory processing.

@@

These are the same stimuli, and we changes these two sentences to better reflect that:

"To test this question, we exposed tadpoles to four hours of behaviorally salient, startle-inducing “click” sounds, provided at the same frequency (every second) as visual stimuli in the first set of experiments. We found (Fig 1D, E) that exposure to these sounds..."

> - Tadpoles are exposed to 4 hours of click sounds and then intrinsic tuning was measured. No difference
in spiking was observed. This was interpreted to mean that acoustic stimuli did “not strongly activate
tectal circuits during conditioning”. How can the authors know this? Instead, why not determine this
directly by recording click-evoked responses from tectal neurons? Or, if tectal cell responses to auditory
stimuli have been described in previous work, this should be included here.

Unfortunately, electrophysiological recording of tectal reponses to sounds in tadpoles does not seem to be technically feasible, not just in our lab (where we don't even have the technical capability to perform in-vivo experiments), but in most labs. From the technical point of view, the problem amounts to two limitations: one, to record from a tadpole, one has to paralyze it with a nicotinic receptor anatagonist, which seems to disrupt hearing. Second, even if this limitation could be overcome, the sounds have to be strong enough to stimulate the inner ear, but weak enough not to mechanically disrupt the recording. Conceivably, both challenges may be circumvented with the use of high speed calcum imaging in freely moving tadpoles, but to our knowledge no lab has attempted these recordings yet.

@@

> Page 6 line 24: Remove the phrase “are not easily interpretable”. Instead, please interpret your data
clearly.

We removed this phrase.

> Page 9: The authors report that the synaptic data show that “prolonged sensory activation with short,
frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective
potentiation of visual inputs from the eye”.
How do the authors know the effect is selective for RGC inputs? It appears that they only measured
RGC-evoked responses. Auditory/mechanosensory -evoked responses were not reported.

Stimulation in the optic chiam evokes two types of synaptic responses in tectal cells: direct short-latency responses, and delayed recurrent inputs from other cells in the tectum. By looking at average currents early and later after the chiasm shock, we can independently assess the contribution of direct and recurrent inputs. In the paper, in a paragraph before the sentence in question, we report that after stimulation, direct input mediated current increased in amplitude, while recurrent input mediated currents remained unchanged. This is what we call selective potentiation of direct inputs, as opposed to recurrent inputs. We do not claim that mechanosensory inputs did not change, as we have not recorded auditory responses in this study (recording of auditory responses is considerably more difficult; see Felch 2016).

To make sure that we are not misunderstood by the reader, we replaced the original sentence with the following two sentences: "This shows that prolonged sensory activation with short, frequent stimuli reshaped synaptic transmission in the tectum, making it faster through selective potentiation of visual inputs from the eye, compared to recurrent inputs within the tectum that remained unchanged. In this study, we did not probe changes in acoustic and mechanosensory projections from the hindbrain."

@@

As described above, we now don't use quotation marks for any basic words, so "preferred" is used without quotation marks, and consistently means "responded preferably", or "produced stronger responses".

> Page 10 (last paragraph): Were action potential thresholds measured? Were there any differences in
this parameter across groups?

The paragraph in question read: "We ran a stepwise generalized linear model selection analysis (R package stepAIC,
Venables and Ripley 2013) to explain the intrinsic tuning of cells recorded in all
experimental groups through these eight variables. We found that the average spikiness
(after compensation for position within the tectum; see Methods) was best described by a
combination of sodium peak current (INa) and membrane resistance (Rm) variables, but
these variables explained only 8% and 2% of cell-to-cell variance respectively
F(1,130)=11.3, and F(1,130)=4.5; Figure 3E)." etc.

We measured action potential thresholds, but did not report them, as we know from earlier studies (Ciarleglio Khakhalin 2015) that AP threshold measurements in tectal neurons are highly sensitive to the current that is used to evoke the spikes, due to rapid Na channel inactivation. At the analysis phase, we briefly tried to use AP thresholds from current clamp experiments to estimate the prominence of Na channel inactivation in individual tectal neurons (Azouz 2000; Fontaine 2014), but these attempts did not lead to conclusive results, and as they are also not based on established analysis methods, they are not reported in the paper. Neither minimal threshold for generating an action potential, nor the slope of AP threshold with increased holding current, were different across groups (ANOVA p=0.7 and 0.3, respectively).

@@

https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/dynamic_other_vars.R

> Page 13, line 7: What does “intrinsic spikiness” mean? Is this another term for intrinsic excitability, or is
this a different parameter? In fact, throughout the manuscript, there are many terms including “intrinsic
excitability, spikiness, number of spikes, and intrinsic spikiness that probably mean the same thing – or
maybe not. If these terms all mean the same thing, then one term should be chosen and used
throughout. If they all refer to different entities, then each one should be clearly defined.

Thank you for making us get more consistent here! In this updated version, we consistently use "spikiness" as a name for the variable that is for the first time introduced in Figure 2C. When writing about the average number of spikes, we now just call it the "average number of spikes", and not "spikiness". As the only exception to this rule, we opted for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text, even though strictly speaking it is a sentence about intrinsic excitability. The expression "intrinsic spikiness" is no longer used. The expression "intrinsic excitability" is now used only as a name for the underlying property of the neuron, that may be probed with different alternative protocols and measures. In this study, we mostly assess intrinsic excitability using a more narrowly defined "spikiness" variable, but towards the end of the paper, we also compare it to a less informative measure of the number of spikes observed in current clamp experiments. We use "intrinsic excitability" when we make inferences about the actual properties of the neuron, and use "spikiness" when we talk about the actual numerical value calculated to assess and quantify intrinsic excitability.

SILAS-SAYS: While you've certainly explained our approach to R2, I wonder if R2 will want us to make the same explicit statements about what each term mean in the manuscript itself.

@@

> Page 15 line 34: The average membrane resistance (330 MOhm) seems a bit low for these small immature
tectal neurons. Were the neurons healthy? What was the average resting membrane potential? Were
there any set criteria for Rm, Vm, or access resistance?

Thank you for catching this error! We had an order of magnitude typo here, as the average membrane resistance was in fact 3.2 GOhm. This value is a bit higher than reported in earlier studies (1.2±0.8 GOhm in Ciarleglio Khakhalin 2015; about 1.1 in Khakhalin 2011), but within what can be reasonably expected for healthy neurons of this size. To make sure that this number is right, for the purpose of this response, we also verified it by reanalyzing our data offline, and obtained a similar estimation for the average membrane resistance (2.9±1.4 GOhm).

We have several reasons to believe that the cells included in this study were healthy. First, the access resistances obtained were good (30±14 MOhm, which is similar to benchmarks of 50±23 in Ciarleglio Khakhalin 2015, and about 20-30 MOhm in Khakhalin 2011), indicating that higher membrane resistance is not likely to be due to poor access. Second, our neurons reliably produced spikes in current clamp mode, and active currents in response to membrane depolarization in voltage clamp mode. Moreover, our quantification of these active conductances yielded numbers similar to those reported before (Ciarleglio Khakhalin 2015). The quality of voltage clamp, as judged by the absence of escaping active currents in IV protocols, was good in the majority of neurons (82% of all neurons recorded). Finally, a few cells that had their membrane resistance change drastically during the recording, were discarded at the data collection stage, and not included in this study.

We did not measure the resting membrane potential directly, but measured the holding current necessary to bring the cell to -60 mV in voltage clamp mode, and the mean value of this I_hold value was -8.2±4.8 pA, which is similar (most importantly, not higher) than what was previously reported in the literature (-19.8±16.6 in Ciearleglio Khakhalin 2015).

@@

Together, these arguments make us believe that the quality of our patches was good enough to draw the conclusions reported in the study. Note that all data for all cells is available here:

https://github.com/khakhalin/Dynamic-clamp-2018/blob/master/Data/data_mainInput.txt

In this full dataset, groups "Naive", "SlowF", and "SlowC" should be ignored, as they were not included in the study. Note also that if you open this file on github, the columns may look misplaced, as github does not render tab-separated files correctly, so if you want to inspect the data, we recommend that you download it and open it in a spreadsheet.

Since the mistake that you noticed (thank you again for being so thorough!) was a typo in the text, and not a mistake in the data, it does not affect any calculations reported in this paper.

@@

> Figure 1 D and E: The average number of spikes fired as a function of conductance duration and all at 3
different peak conductances. Are there any trends at the single cell level? For example, if a given
control neuron fires relatively few spikes in response to 500 ms duration, does it also tend to fire
relatively fewer spikes with 1000ms duration? Or maybe if a given neuron fires a relatively high number
of spikes with 500ms then it will typically fire less at 1000ms duration? Although the individual
responses are shown in 1D, it is impossible to follow the number of spikes fired by any individual neuron
in response to the different conductance durations.

At least for high-spiking neurons, the answer to this question can be inferred from Figure 1D: those curves that are placed high on the graph for duration of 500 ms, also tend to remain high for 1000 ms, indicating that high-spiking neurons tend to be high-spiking across the range of durations. Numerically, the correlation coefficient between the average number of spikes in response to 500 and 1000 ms, across all neurons, is r=0.94. This is to be expected, as intrinsic excitability of neurons (whether the neuron is spiky or not) is a much stronger feature than the temporal tuning. (Temporal tuning in the tectum was not even described until this paper, while the variation in intrinsic excitability in the tectum is well known for more than 20 years).

SILAS-SAYS: It seems R2 is asking if most cells follow the pattern of spike increase with duration increase as highlighted by the mean, or if the sum of many different activation patterns just happens to generate that average. I think that your point about the correlation coefficient puts that to rest, but you may want to say that more explicitely because it is legitimately difficult to look at the individual data points to this level of precision without seeing the mean trend.

### 2019-06-06 reviews and responses.md

> Page 5, line 45/46: “As one possible explanation, auditory and mechanosensory inputs may have
different cellular or subcellular 46 targets in the tectum (Bollmann and Engert, 2009).”
This Bollmann and Engert reference does not address mechanosensory and auditory inputs. This paper
shows that the RGC inputs form a topographic map along the proximal-distal axis of individual tectal
neuron dendrites. This reference should be replaced with an appropriate reference.

> Also, how can having different subcellular targets could explain the results? This concept needs to be
clarified – an example would be helpful.

We replaced this sentence with the following one: "This was not necessarily surprising, as mechanosensory and visual inputs have different cellular targets in the tectum (Pratt and Aizenman, 2009; Felch et al., 2016; Truszkowski et al., 2017), potentially leading to different recruitment of tectal excitatory and inhibitory circuits. Acoustic stimuli may also be inherently weaker than visual stimuli in triggering plasticity effects in tectal neurons, as they arrive at different compartments within the dendritic tree (Hiramoto and Cline, 2009; Deeg et al., 2009), which may shape their influence on neuronal plasticity (Richards and Lillicrap, 2019)."

Here, the actual rationale for the second explanation (a difference in subcellular targets) is that inputs to different parts of the dentritic tree can trigger action potentials of different shape, and differentially affect calcium dynamics in the neuron, which, together with non-linear processing in dendrites may make different types of inputs unequal in terms of their effects on neuronal activity, and neuronal tuning, respectively. Two extreme examples of this effect would be the impact of climbing fibers on the activity of Purkinje cells in the cerebellum, or the impact of inputs to the apical dendrites of pyramidal cells in the cortex. We feel, however, that this topic is very complex, yet somewhat tangential to the main message of the paper, so we tried to limit our exposition into it by a short sentence and a good, recent reference.

@@

"We then examined whether different types of sensory activation would differentially reshape  
temporal intrinsic tuning in tectal neurons. As changes in intrinsic properties seemed  
homeostatic (increased activation led to reduced spiking), by the same logic, one could
expect shorter stimuli (flashes) to selectively suppress responses to shorter synaptic inputs."

Here we are not implying that our conditional stimuli altered the pattern of synaptic inputs; rather, we refer to the fact that _during_ the stimulation, shorter stimuli (such as instantaneous flashes, which technically makes them the shortest stimuli possible) would cause faster visual inputs to the tectum, compared to longer, continuous transitions (second-long looms). Within this study, we did not measure actual synaptic responses in the tectum during conditioning, but from previous studies, we know that responses to flashes are indeed much shorter than responses to looming stimuli (Khakhalin 2014, Khakhalin 2019). We refer to these studies in the beginning of the "Results" section, and then again in the "Methods".

For page 5, we now changed the wording, to make this logic clearer.

"We knew from earlier studies that fast tectal responses can be evoked with instantaneous flashes, while looming stimuli cause slower, and more prolonged tectal activation (Khakhalin et al., 2014; Khakhalin, 2019). As overall changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to flashes would selectively suppress spiking in1response to fast synaptic inputs."

@@

With the new wording of this sentence, we tried to make this point more clear:

"We knew from earlier studies that fast tectal responses can be evoked with instantaneous flashes, while looming stimuli cause slower, and more prolonged tectal activation (Khakhalin et al., 2014; Khakhalin, 2019). As overall changes in intrinsic properties seemed homeostatic (increased activation led to reduced spiking), by the same logic, one could expect that exposure to flashes would selectively suppress spiking in1response to fast synaptic inputs."

> Page 5 line 15: Does the word “preferred” (in quotes) mean that the cells fired more action potentials?
Maybe refrain from personification.

We hope that the word "prefer" is intuitive, and it has a benefit of being way shorter than "responded with more spikes", or "produced more action potentials", which hopefully makes reading easier. Realistically, we hope that most readers of this article will not be at risk of truly personifying neurons, so while we take care to never personify animals, we are intentionally a bit more relaxed when writing about cells, channels, receptors etc. Still, to make this sentence better, we removed the quotes around "preferred", to make it more obvious that it is not an antropomorphic allegory, but just a normal word use, and also added a clarification:

"In other words, while control neurons preferred longer inputs (responded to them with more spikes), stimulated neurons developed a preference for shorter synaptic inputs..."

Overall, we use the word "prefer" 6 times in the paper, always in the same way: when comparing spiking responses to different stimuli, to describe the stimulus that produced sronger outputs in a given set of neurons.

### 2019-06-06 reviews and responses.md

We improved the sentence:

"Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E), as they did not increase their spiking as fast in response to larger conductances."

> - Excessive wordiness makes the results difficult to read and interpret. For example,
on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
between temporal tuning and synaptic duration implies a co-tuning of preferr
parameters.”

Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3. The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in a good faith replace them with one sentence, as the statement we make there is not statistically obvious. We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair. The issue, as we describe it, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes. Had the slopes been the same, we would have just reported a correlation in one sentence. But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is not uncommon for large datasets, but that some readers may not be intimately familiar with.

We are aware that this section may read differently for different readers, and we received some conflicting advice in the past, about the level of details that is optimal for communicating this message. For example, readers who discussed Simpson's paradox in their statistics classes typically find our mentioning of this term helpful, while those who haven't encountered this term before, tend to find it distracting. For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience. Nevertheless, in this new version of the paper, we shortened this section from 411 to 294 words.

@@

We are not sure how this fact can be illustrated. We searched for papers that use stepwise linear models, and it seems that researchers do not typically include summary figures to describe combinatorial model optimization. Some papers that use this method include tables, listing R-squared, F, df, and p-values for every component, but as in our paper we are not particularly concerned with the precise composition of the model, we are not sure that a table like that would be useful. If you have some specific type of illustration in mind, please kindly describe it, or reference it. The only type of illustration we could come up with is a scatterplot that compares values predicted by the model to actual values, as shown on Figure 4E. Some technical papers sometimes also present the model information factor penalty as a function of the number of terms included in the model, but again, we are not sure how useful this type of presentation would be for our paper, as we are not particularly concerned with the composition of the model, and the quality of the information criterion minimum, as our main point here is that the prediction quality of this whole family of models is not great, and we cannot even overfit, as temporal tuning cannot be predicted from standard voltage-clamp-based electrophysiological variables.

For references, see for example: Stine, R. A. (2004). Model selection using information theory and the MDL principle. Sociological Methods & Research, 33(2), 230-260.

> - If these data are interpreted as homeostatic (neurons became less excitable
following sensory experience), is there any evidence that tectal neurons have
different firing activities during the different kinds of sensory experience? For
example, does sound engage tectal neurons less than visual stimuli, and might this
explain some of the trends in the data?

This may indeed explain some of the trends in the data, but unfortately, as we described above, recording of tadpole tectal reponses to sounds does not seem to be possible in our lab, and is fundamentally technically problematic in principle. We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics are drastically different, and as they engage different circuits before reaching the tectum (retinal circuits for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019). We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of the Discussion, by describing how our observations can be used to predict actual, unobserved activation of the tectum during multisensory stimulation in vivo:
